Applying Pose Estimation to Predict the Outcome of Basketball Shots

### 2022-11-30 Papers/Report/report.tex
Start results section

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

>>>>

\section{Results}
In this section, we present and discuss in detail the results of our experiments. In all of these experiments, we used MoveNet as our pose estimator and Catboost
Gradient Boosting Tree as our classification model, as explained in the previous section.
\subsection{First Approach to Feature Vector Generation}
In our first experiment, did a more extensive test on our first approach to feature vector generation. In our preliminary test,
we did not use our full set of data, as we generated more data after this preliminary experiment. Additionally, we would like to evaluate
the model on ROC-AUC score. Lastly, as we repeatedly retrained and reevaluated the model, we were getting performance scores that varied 
to some extent. Because of this, we decided to create a sample distribution of ROC-AUC scores we achieved for each iteration of our model. To do this,
we ran our model 100 times, each with a randomized train-test split. We then recorded each ROC-AUC score and plotted the histogram of the scores.
%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}
